Random Forests", OAs

### 2025-02-09 src/oa_RF.Rmd
oa

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    4.999920  0.2053697  1.047293
#   2     extratrees  5.167655  0.1540213  1.103048
#   5     variance    5.187039  0.1710128  1.034382
#   5     extratrees  5.169570  0.1557868  1.122845
#   8     variance    5.633427  0.1247189  1.035171
#   8     extratrees  5.182860  0.1563555  1.137332
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule =
#  variance and min.node.size = 5.

varimp_mars <- varImp(model.all) 
varimp_mars$importance <- varimp_mars$importance %>% 
  rownames_to_column() %>% 
  mutate(rowname = ifelse(rowname == "dist", "distance to the nearest city",
                          ifelse(rowname == "dist.retail", "distance to the nearest retail centre", 
                                 ifelse(rowname == "London", "distance to London",
                                        ifelse(rowname == "n.nearest.retail.lag", "Nearest retail centre's wensite density, t-1",
                                               ifelse(rowname == "n.London.lag", "London's wensite density, t-1",
                                                      ifelse(rowname == "n.l.slag", "spatial and temporal lag of wensite density",
                                                             ifelse(rowname == "n.nearest.city.lag", "Nearest city's wensite density, t-1", rowname)))))))) %>% 
  column_to_rownames()

>>>>

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    4.644230  0.2444898  1.236831
#   2     extratrees  4.874616  0.1642528  1.207521
#   5     variance    4.716793  0.2415236  1.251176
#   5     extratrees  4.779489  0.2006192  1.294454
#   8     variance    5.257495  0.1919632  1.262540
#   8     extratrees  4.814190  0.1951799  1.311195
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance
#  and min.node.size = 5.
#  
varimp_mars <- varImp(model.all) 
varimp_mars$importance <- varimp_mars$importance %>% 
  rownames_to_column() %>% 
  mutate(rowname = ifelse(rowname == "dist", "distance to the nearest city",
                          ifelse(rowname == "dist.retail", "distance to the nearest retail centre", 
                                 ifelse(rowname == "London", "distance to London",
                                        ifelse(rowname == "n.nearest.retail.lag", "Nearest retail centre's wensite density, t-1",
                                               ifelse(rowname == "n.London.lag", "London's wensite density, t-1",
                                                      ifelse(rowname == "n.l.slag", "spatial and temporal lag of wensite density",
                                                             ifelse(rowname == "n.nearest.city.lag", "Nearest city's wensite density, t-1", rowname)))))))) %>% 
  column_to_rownames()
